---
title: "BIOL 432 Assignment 3"
output:
  pdf_document:
    toc: FALSE
  html_document:
    toc: TRUE
---

### Project Info 

[Github repository (link)](https://github.com/ameliems99/A3_BIOL_432)  
**Date:** 25/01/2022  
**Author:** Amelie Mahrt-Smith, 20054398  
**Github user:** ameliems99  

### Data Wrangling   
  
Load required packages:
```{r message = FALSE}
library(dplyr) 
```

Load and 'wrangle' data:
```{r}
Fallo <- read.csv("./InputData/FallopiaData.csv") %>%
  filter(Total >= 60) %>%  #remove rows with Total Biomass <60
  select(Total, Taxon, Scenario, Nutrients) %>%  #Keep only these columns, in this order
  mutate(TotalG = Total/1000, Total = NULL) %>%  #replace Total with TotalG
  select(TotalG, everything())  #re-order columns to put TotalG first
```


### Custom Function

Function:   

'a3_func()' takes two inputs from the user: a vector of data specified by 'var', and a string defining a calculation to perform specified by 'calc'. The function can calculate the mean, sum, or number of observations of the vector; all other operations result in error. 
```{r}
a3_func <- function (var = 0, calc = ""){ 
  if (calc == "Average"){
      return(mean(var))
  } 
  if (calc == "Sum"){
    return(sum(var))
  }
  if (calc == "Observations"){
    return(length(var))
  }
  else {
    print("Error in 'calc': invalid argument")
  }
}
```

Example: 
```{r}
a3_func(Fallo$Taxon, "Observations") #count the number of observations in 'Taxon' column

FalloL <- filter(Fallo, Nutrients == "low")
FalloH <- filter(Fallo, Nutrients == "high")
cat("Low nutrients average biomass (g) = ", a3_func(FalloL$TotalG, "Average"), 
      "\nHigh nutrients average biomass (g) = ", a3_func(FalloH$TotalG, "Average")) #calculate average 'TotalG' for each 'Nutrient' concentration
```


### Output 
```{r}
write.csv(Fallo, "./Output/WrangledData.csv")
```
